How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-28 Manuscript.tex
Updates from ShareLaTeX

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). Then, the performance was measured using standard benchmarking tools (delivered by \textsc{Oracle} for Berkley data sets and other popular tools such as \textsc{autobench} and \textsc{httpref})~\cite{sven12}. It's worth noting that in each of the above data set, some configurations are interdependent, this is expressed using a \textit{feature model}.
   \fig{bdbc} shows an example of such a feature model defining valid combinations of settings to on the Berkley database (``C'' version). These feature models were used by Siegmund et al. to ensure all their perturbations are valid
   (we will use the same models to cull invalid plans).

>>>>

  The Siegmund data, described in \fig{cpm},  records  the runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). Then, the performance was measured using standard benchmarking tools (delivered by \textsc{Oracle} for Berkley data sets and other popular tools such as \textsc{autobench} and \textsc{httpref} for the rest)~\cite{sven12}. It's worth noting that in each of the above data set, some configurations are interdependent, this is expressed using a \textit{feature model}.
   \fig{bdbc} shows an example of such a feature model defining valid combinations of settings to on the Berkley database (``C'' version). These feature models were used by Siegmund et al. to ensure all their perturbations are valid
   (we will use the same models to cull invalid plans).

### 2015-08-28 tex/results_models.tex
Updates from ShareLaTeX

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &          HOW &    -3.3  &  2.2 & \quart{26}{2}{27}{32} \\
  1 &      baseln0 &    -2.9  &  11.7 & \quart{17}{14}{28}{32} \\
  1 &      baseln1 &    -2.75  &  65.5 & \quart{0}{78}{28}{32} \\
\hline  2 &        dtree &    51.5  &  14.84 & \quart{82}{17}{93}{32} \\
\end{tabular}}
\caption{Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when other planners fail to do so.
}\label{fig:coc}
\end{figure}

>>>>

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &          BIC &    -3.3  &  2.2 & \quart{26}{2}{27}{32} \\
  1 &      CD &    -2.9  &  11.7 & \quart{17}{14}{28}{32} \\
  1 &      CD+FS &    -2.75  &  65.5 & \quart{0}{78}{28}{32} \\
\hline  2 &        XTREE &    51.5  &  14.84 & \quart{82}{17}{93}{32} \\
\end{tabular}}
\caption{Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when other planners fail to do so.
}\label{fig:coc}
\end{figure}
